An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-14 EconGrowth-R-Functions.Rnw
Now creating lattice partial residual plots for all countries. Need to format them a bit better, but they are working at least.

<<PartialResidualPlots, eval=TRUE>>=
#################
# Creates a plot with y residuals vs. energy (e). The y residuals are from the specified modelType without energy.
# modelType: one of "CD" or "CES"
# energyType: one of "Q", "X", or "U"
# The energy term on the x axis is whatever type is specified in the calling funciton
# 
partialResidualPlot <- function(modelType, countryAbbrev, energyType, textScaling=1.0){
  if (modelType == "CD"){
    model <- cdModel(countryAbbrev)  
  } else if (modelType == "CES"){
    model <- cesModelNoEnergy(countryAbbrev)
  } else {
    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
  }
  # Get the model
  # Get the residuals
  resid <- resid(model)
  resid <- data.frame(resid)
  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
  # Load data
  data <- loadData(countryAbbrev)
  data <- cbind(data, resid)
  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
  plot <- xyplot(resid ~ iEToFit, data=data,
                 type=c("p"),
                 col="black",
                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
                 )
  return(plot)  
}

partialResidualLattice <- function(modelType, energyType){

}
@

>>>>

<<PartialResidualPlots, eval=TRUE>>=
#############################
# Creates a data.frame containing raw data and residuals for given arguments.
# modelType: one of "CD" or "CES"
# countryAbbrev: the country of interest to you
# energyType: one of "Q", "X", or "U"
##
calcResiduals <- function(countryAbbrev, modelType, energyType){
  # Get the model
  if (modelType == "CD"){
    model <- cdModel(countryAbbrev)  
  } else if (modelType == "CES"){
    model <- cesModelNoEnergy(countryAbbrev)
  } else {
    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
    return(NULL)
  }
  # Get the residuals
  resid <- resid(model)
  resid <- data.frame(resid)
  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
  # Load data
  data <- loadData(countryAbbrev)
  data <- cbind(data, resid)
  # Replace name of column we want with the name "iEToFit"
  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
  return(data)
}

#################
# Creates a plot with y residuals vs. energy (e). The y residuals are from the specified modelType without energy.
# modelType: one of "CD" or "CES"
# energyType: one of "Q", "X", or "U"
# The energy term on the x axis is whatever type is specified in the calling funciton
# 
partialResidualPlot <- function(modelType, countryAbbrev, energyType, textScaling=1.0){
  data <- calcResiduals(modelType=modelType, countryAbbrev=countryAbbrev, energyType=energyType)
  plot <- xyplot(resid ~ iEToFit, data=data,
                 type=c("p"),
                 col="black",
                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
                 )
  return(plot)  
}

partialResidualLattice <- function(modelType, energyType, textScaling=1.0){
  data <- do.call("rbind", lapply(countryAbbrevs, calcResiduals, modelType=modelType, energyType=energyType))
print(data)
  plot <- xyplot(resid ~ iEToFit | Country, data=data,
                 type=c("p"),
                 col="black",
                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
                 )
  return(plot)
}

### 2013-04-14 EconGrowth.Rnw
Now creating lattice partial residual plots for all countries. Need to format them a bit better, but they are working at least.

<<CDPartialResidualsQ, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
partialResidualPlot(modelType="CES", countryAbbrev="US", energyType="Q")
@

>>>>

<<CDPartialResidualsQ, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
partialResidualPlot(modelType="CD", countryAbbrev="US", energyType="Q")
partialResidualLattice(modelType="CD", energyType="Q")
@
